Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-06-03 analysis/sim/run_simpw.Rmd
sims dome

652 4---
title: "Examining background gene lists using simulation - comparison of different enrichment techniques"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
theme: cosmo
---

@@

#library("tidyverse")
library("parallel")
library("edgeR")
library("DESeq2")
library("limma")
library("stringi")
library("kableExtra")
library("fgsea")
library("clusterProfiler")
source("simpw_func.R")

@@

@@

gsets <- randomGeneSets(a,setsize=20,nsets=200)

@@

SIMS=100
FRAC_DE=0.05
FC=1
N_REPS=6
DGE_FUNC="deseq2"
SUM_COUNT=3e7
VARIANCE=c(0.3,0.35,0.4,0.45)

@@

```{r,results}

@@

cp <- subset(res,PWAY_FUNC == "clusterprofiler")
fo <- subset(res,PWAY_FUNC == "fora")
fg <- subset(res,PWAY_FUNC == "fgsea")

>>>>

---
title: "Examining background gene lists using simulation - comparison of different enrichment techniques"
author: "Mark Ziemann & Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
theme: cosmo
---

@@

library("parallel")
library("edgeR")
library("DESeq2")
library("limma")
library("stringi")
library("kableExtra")
library("fgsea")
library("clusterProfiler")
source("simpw_func.R")

@@

19. mitch up

20. mitch dn

@@

gsets <- randomGeneSets(a,setsize=30,nsets=200)

@@

SIMS=500
FRAC_DE=0.05
FC=1
N_REPS=5
DGE_FUNC="deseq2"
SUM_COUNT=2e7
VARIANCE=c(0.3,0.325,0.35,0.375,0.4,0.425,0.45)

@@

```{r,rqesults}

@@

cp <- subset(res,PWAY_FUNC == "clusterprofiler")
fo <- subset(res,PWAY_FUNC == "fora")
fg <- subset(res,PWAY_FUNC == "fgsea")
mi <- subset(res,PWAY_FUNC == "mitch")
